\begin{acknowledgements}

I am humbled to acknowledge those who have made this work possible through their kindness and support, and those who took a chance on me and gave me an opportunity to succeed.

I'd like thank my family for their love and support.

I'd like to thank my advisor Gillian Wilson for her support and direction, for the opportunity she provided, and for the data.
Thanks to my collaborators Andrew Degroot, Adam Muzzin, and Mike Cooper, who provided helpful advice and feedback on my research.
Thanks to my undergraduate research advisor Rafael Garcia, for driving me to excel, and for instilling in me an appreciation for the finer points of physics.
Thanks to my mentor, Steve Corman.
Thanks to Naveen Reddy and Laura Sales for being members of my dissertation committee.

I'd like to thank Katie Curnyn, and my classmates Evan Sosenko, William Freeman, Kira Burt, Kennedy Elizabeth, Bobby Schafer, Irene Shivaei, Calvin Cordozar Broadus, Jr., and Shaolong Chen.

I'd like to thank the staff of the Chandra Director's Office: Harvey Tananbaum, Belinda Wilkes, Paul Green, Andrea Prestwich, and Nancy Evans.
My life has been shaped dramatically by the opportunity they selflessly afforded me.

I especially thank all of my friends.
Over the years they have fed and sheltered me, and enthusiastically believed in me.
I could not have done this without them.

The data presented in this work were obtained at the W.M. Keck Observatory, which is operated as a scientific partnership among the California Institute of Technology, the University of California and the National Aeronautics and Space Administration. The Observatory was made possible by the generous financial support of the W.M. Keck Foundation. I would like to recognize and acknowledge the very significant cultural role and reverence that the summit of Mauna Kea has always had within the indigenous Hawaiian community.  We are most fortunate to have the opportunity to conduct observations from this mountain.

\end{acknowledgements}
